\pkg{sparseHessianFD}: An R Package for Estimating Sparse Hessian Matrices

### 2016-12-25 nobuild/jss_revision/sparseHessianFD.tex
checking with win-builder

\end{tabularx}
\caption{Computation times (milliseconds) for computing Hessians using the
  \pkg{numDeriv} and \pkg{sparseHessianFD} packages, and the finite
 difference and complex step methods, across 200 replications. Rows are ordered by the
  number of variables.}\label{tab:numDeriv}
\end{table}

To help us understand just how scalable
\pkg{sparseHessianFD} is, we ran another set of simulations, for the
same hierarchical model, for different values of $N$ and $k$.  We then
recorded the run times for different steps in the sparse Hessian
estimation, across 500 replications.  The steps are summarized in
Table~\ref{tab:timeMeasures}.  The times were generated on an
Apple Mac Pro with a 12-core Intel Xeon E5-2697 processor (2.7 GHz)
with 64 GB of RAM.

>>>>

\end{tabularx}
\caption{Computation times (milliseconds) for computing Hessians using the
  \pkg{numDeriv} and \pkg{sparseHessianFD} packages, and the finite
 difference and complex step methods, across 500 replications. Rows are ordered by the
  number of variables.}\label{tab:numDeriv}
\end{table}

To help us understand just how scalable
\pkg{sparseHessianFD} is, we ran another set of simulations, for the
same hierarchical model, for different values of $N$ and $k$.  We then
recorded the run times for different steps in the sparse Hessian
estimation, across 200 replications.  The steps are summarized in
Table~\ref{tab:timeMeasures}.  The times were generated on an
Apple Mac Pro with a 12-core Intel Xeon E5-2697 processor (2.7 GHz)
with 64 GB of RAM.
